More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-05-22 2016-Weak-FH-Bisim/WeakBisim.tex
reunion avec rabea

We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t. $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
\def\WT{\mathcal{WT}}
\begin{definition}[Weak open transition]\label{def:weakOT}
A weak open transition over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
\begin{mathpar}
 \openrule
         {
           \gamma_j^{j\in J},\symb{True},Id(s)}
         {s \OTWeakarrow {\alpha} s}
 \end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\gamma_j$
        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

 \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
      covered by a set of weak transitions from $s$ in $\mathcal{T}_1^*$.
 \end{itemize}

Two pNets are Weak FH-bisimilar if there exist a relation between their associated open
automata that is an Weak FH-bisimulation and their initial states are equivalent.
\TODO{LUDO: define equivalent}
 \end{definition}

>>>>

We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t. $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
\def\WT{\mathcal{WT}}
\begin{definition}[Weak open transition]\label{def:weakOT}
A weak open transition over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
\begin{mathpar}
 \openrule
         {
           \gamma_j^{j\in J},\symb{True},Id(s)}
         {s \OTWeakarrow {\alpha} s'}
 \end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\gamma_j$
        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

 \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
      covered by a set of weak transitions from $s$ in $\WT_1$.
 \end{itemize}

Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is true.
 \end{definition}
